Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-07-14 text/manuscript-full-KS.qmd
update figure + landscape page

```{=tex}
\endgroup
\doublespacing
\clearpage
```
<!-- TABLES -->

```{r fig-chicago-recruiting, echo = FALSE, fig.align = 'center', fig.cap = "The College Board Enrollment Planning Service Chicago Geomarkets (left) and University of Chicago Recruiting Territories (right)", out.width = "85%"}
knitr::include_graphics('./../assets/images/chicago_recruiting.png')
#knitr::include_graphics('./../../outputs/figures/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

@@

```{r fig-geomarket-methods, echo=FALSE,out.width="49%", fig.cap="caption",fig.align='center',fig.cap = "Chicago, College Board and Recreated Geomarkets"}
knitr::include_graphics('./../assets/images/eps/chicago_geos.png')

@@

@@

>>>>

```{=tex}
\endgroup
\doublespacing
\clearpage
\pagenumbering{gobble}
```
<!-- TABLES -->

::: {.landscape}

```{r fig-chicago-recruiting, echo = FALSE, fig.align = 'center', fig.cap = "The College Board Enrollment Planning Service Chicago Geomarkets (left) and University of Chicago Recruiting Territories (right)", out.width = "100%"}
knitr::include_graphics('./../assets/images/chicago_recruiting.png')
#knitr::include_graphics('./../../outputs/figures/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

:::

@@

::: {.landscape}

```{r fig-geomarket-methods, echo=FALSE,out.width="100%", fig.cap="caption",fig.align='center',fig.cap = "Chicago, College Board and Recreated Geomarkets"}
knitr::include_graphics('./../assets/images/eps/chicago_geos.png')

@@

:::

@@

::: {.landscape}
